References for PloS paper

### 2014-02-19 image_analysis_paper/background_reading/article_notes.tex
added updates to background reading notes

\item \fullcite{li2009stochastic}

@@

\item \fullcite{peng2013detecting}

\item \fullcite{gerber2010visual}

\item \fullcite{qiu2011discovering}

\item \fullcite{gupta2008extracting}

\item \fullcite{lau2009modeling}

\item \fullcite{toga2003temporal}

\item \fullcite{li2012modelling}

\item \fullcite{denkinger2013set}

\item \fullcite{xu2012comprehensive}

\item \fullcite{sisan2010event}
\begin{itemize}
	\item Looks at time correlations in data to determine temporal ordering
	\item Goal is to determine in what order cellular events happen (i.e. does rxn A lead to rxn B, or does B lead to A)
	\item They look at the time-correlation between events.
	\item Asymmetry in time-correlation tells you in what order events happen (depending on model)
	\item Looking at time correlation over many samples integrates/averages out stocahsticity in system
\end{itemize}

@@

>>>>

\item \fullcite{li2009stochastic}
\begin{itemize}
	\item Want to look at mechanism for {\em eve} stripe formation
	\item Propose a large gene/protein interaction network
	\item Use maximum likelihood to prune the network and find the most probable network that would give rise to the observed spatiotemporal dynamics
\end{itemize}

@@

\item \fullcite{peng2013detecting}
\begin{itemize}
	\item Wants to find which genes/SNPs are responsible for variation in facial features
	\item Has DNA data and 3D face scans for many samples
	\item Looks at different facial models (all are based on landmarks)
	\item Tries to find which variations in the facial models correlate with which SNPs
\end{itemize}

\item \fullcite{gerber2010visual}
\begin{itemize}
	\item Want to find a ``good'' way to visualize high--dimensional functions
	\item First find local maxima and minima in data set
	\item Use these maxima and minima to segment the domain of the function into ``crystals''
	\item Approximate each crystal by a line/curve
	\item Embed the maxima and minima in 2D using PCA; draw lines connecting relevant maxima and minima
\end{itemize}

\item \fullcite{qiu2011discovering}
\begin{itemize}
	\item Want to order microarray data
	\item Look at specific (high--variance) genes (~3000 genes)
	\item Cluster genes into ``modules'' using k--means, so that similairly expressed genes are grouped together
	\item Within each module, construct a minimium spanning tree of the data (distance between nodes is Euclidean distance)
	\item Find set of MSTs that are most similar/consistent
	\item Assume these are the ``right'' MST and that they uncover the progression of the data
\end{itemize}

\item \fullcite{gupta2008extracting}
\begin{itemize}
	\item Want to temporally order gene expression data from cancer patients
	\item Use TSP to order gene expression data (can show that TSP path will recover the correct ordering under some probability model)
	\item Use a probabilistic gene/patient model to model the variation from patient to patient (model underlying dynamics with splines, and then assume rest in noise from patient-to-patient variability)
\end{itemize}

\item \fullcite{lau2009modeling}
\begin{itemize}
	\item Want to model trajectory/motion data where each sample is a trajectory
	\item Assume that the trajectories come from a second-order Markov model (i.e. $t+2$ depends on $t$ and $t+1$)
	\item Fit a Bayesian network that models the trajectory evolution using training data
	\item Can then produce new sample trajectories from this Bayesian network
\end{itemize}

\item \fullcite{toga2003temporal}
\begin{itemize}
	\item Want to model spatiotemporal changes in the 3D structure of the brain (so that one can detect disease, etc.)
	\item Model growth of different portions of the brain using deformation mapping (look at deformation of different regions of a {\em single} person's brain from one scan to the next)
	\item Can fit cortical models for each person in a population; can then look at variations across these models
\end{itemize}

\item \fullcite{li2012modelling}
\begin{itemize}
	\item Want to use cross--sectional data to model disease progression
	\item Data are things that are known to be important/telling for that particlular disease (i.e. breast cancer data contains descriptors of cell morphology, Parkinson's disease data contains descriptors of speech patterns)
	\item Create ``pseudo time series'' by subsampling data, and from each subsample, finding shortest path that goes from a healthy sample to a diseased sample
	\item From these pseudo time series, can fit a hidden Markov model to find different states of disease progression and likely transitions from one state to another
\end{itemize}

\item \fullcite{denkinger2013set}
\begin{itemize}
	\item Want to develop a standardized data set that can be used to investigate temporal and causal neural processing
	\item Developed a set of 222 images which contain different causal and temporal relationships
\end{itemize}

\item \fullcite{xu2012comprehensive}
\begin{itemize}
	\item Want to quantify shape of liver lesions
	\item Take set of 14 common shape descriptors
	\item Use regression to find optimal combination of shape descriptors that can predict the similairity using a ``similairity reference standard''
	\item FINISH
\end{itemize}
\item \fullcite{sisan2010event}
\begin{itemize}
	\item Looks at time correlations in data to determine temporal ordering
	\item Goal is to determine in what order cellular events happen (i.e. does rxn A lead to rxn B, or does B lead to A)
	\item They look at the time-correlation between events.
	\item Asymmetry in time-correlation tells you in what order events happen (depending on model)
	\item Looking at time correlation over many samples integrates/averages out stocahsticity in system
\end{itemize}

@@

\item \fullcite{basu2014detecting}
